%???????????????
\documentclass[11pt, letterpaper, onecolumn, oneside, final]{article}

\usepackage{lab}
\usepackage{soul}

\newfontfamily{\consolas}{Consolas}
[Extension = .ttf]
%\usepackage{fontspec}

\DocumentTitle {Lab 5B}
\DocumentSubtitle {Final Project?}
% End of preamble

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle

% MAKE SURE TO SAVE THIS LAB IN A LABS FOLDER
% LISTS/FOR LOOP QUESTIONS -------------------------------------------
\section{Introduction.} As this is the final week of classes, you will be working on you final project today. As some students may be farther along than others, you will not be expected to reach the end of this lab, but will be expected to make some progress. This will mostly consist of having checkpoints in the lab to display to the TAs/Professor what you have accomplished in class. You should use this time as a TA session: if you get stuck, ask for help. Take advantage of these resources now, since they will not be as readily available in the coming weeks. 
\begin{enumerate}
    \item Discuss with a partner or TA where you are currently at in your project. Make a note here of any questions you may have about the work you have already done. Keep track of where you currently are in your project and where you aim to be by the end of today.\\\\\\
    \item Identify a piece of the project that you would like to work on during today's lab. Write down some ideas in the space below. How will you implement this? Do you need any helper functions? 
    \\\\\\
    \item Code the part of the project you identified in the previous question and show/explain your work to a TA when you complete it.
    
    
    \item If you accomplished you first goal identify a more complicated long term goal you have for your project and like before make note of it below.\\\\\\
    
    
    \item Work on the goal you defined above. It is likely you will not finish this by the end of the lab so don't worry about finishing just focus on making progress.
    
    \item If you have somehow managed to do an incredible amount of work in this lab and or have already finished your project try to come up with aspects to add to your project that improves the overall functionality. This could be how visually appealing your data is or just another degree of analysis.
    
    \item If you managed to get this far, please speak to your professor or a TA on what to do next
    .
\end{enumerate}
% Recursion
\end{document}