\documentclass[11pt, letterpaper, onecolumn, oneside, final]{article}


\usepackage{handout}
\usepackage{soul}

\newfontfamily{\consolas}{Consolas}[Extension = .ttf]

\DocumentTitle {Project 2}
\DocumentSubtitle {Text Analysis}
% End of preamble

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
    \maketitle
\section{Assignment Goals.} 
In this assignment, the students will be expected to demonstrate their understanding of the following concepts:
\begin{itemize}
\item \textbf{The {\consolas nltk} \& {\consolas matplotlib} modules}
\begin{itemize}
\item Students will gain an understanding of text manipulation and data analysis in these two libraries. Students should be able to use these packages in a broader range of applications, outside of their computer science courses.
\end{itemize}
\item \textbf{Booleans \& control flow}
\begin{itemize}
\item Students should demonstrate skills with advanced logic and Boolean statements. Students should also demonstrate skills with constructs like while loops and nested if statements.
\end{itemize}
\item \textbf{Advanced looping structures}
\begin{itemize}
\item Students will be able to create and implement their own while loops and for loops to serve a variety of purposes and maximize the efficiency for their code writing.
\end{itemize}
\item \textbf{Basic data analysis}
\begin{itemize}
\item Students should learn from this project how to parse large data sets (in this case text from books) and pull out relevant data for the specific task they are trying to achieve.
\end{itemize}
\item \textbf{Input/Output Streams}
\begin{itemize}
\item Students will create an interactive menu to call their functions. They must have an understanding of handling input from the standard input stream to generate any type of output for this project. All program control and flow will be determined by this menu and the user.
\end{itemize}
\item \textbf{Function definition \& use}
\begin{itemize}
\item Students should demonstrate an understanding of function definition and implementation as a means to streamline code. Must be able to create and use their own functions that require one or more parameters. Must be able to create and call their own functions to create a working, interactive menu. 
\end{itemize}
\end{itemize}
Through the code they submit, as well as in their grading meeting, they should be able to demonstrate their understanding of the code that they wrote and the aforementioned computer science principles to at least a satisfactory degree.\\
\\
In order to complete the project, students should be taught the following concepts:
\begin{itemize}
    \item More complex control flow constructs (while loops, nested if, elif, else, $\dots$)
    \item Boolean logic
    \item {\consolas nltk} \& {\consolas matplotlib} modules
    \item Input/Output Basics
    \item Basics of function definition and use
    \item String manipulation and methods
\end{itemize}

\end{document}
