\documentclass[11pt, letterpaper, onecolumn, oneside, final]{article}


\usepackage{handout}
\usepackage{soul}

\newfontfamily{\consolas}{Consolas}[Extension = .ttf]

\DocumentTitle {Project 4}
\DocumentSubtitle {Image Manipulation}
% End of preamble

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
    \maketitle
\section{Assignment Goals.}
In this assignment, the students will be expected to demonstrate their understanding of the following concepts:
\begin{itemize}
\item \textbf{2D Arrays}
\begin{itemize}
    \item Students will gain an understand of what grids are and how to use them. They will understand working with grids through various means such as indexing and manipulating grids to a significant extent.
\end{itemize}

\item \textbf{The {\consolas pillow} module}
\begin{itemize}
    \item Students will gain an understanding of image and pixel manipulation in this library.
     Students should be able to use this package in a broader range of applications, and gain an appreciation for the value of coding-based image processing as opposed to preexisting image processing applications. 
\end{itemize}
\item \textbf{Advanced Looping Structures} 
\begin{itemize}
    \item Students should be familiar with advanced looping, specifically nested for loops, and should understand their implementation and how to use them.
\end{itemize}
\item \textbf{Digital Imaging}
\begin{itemize}
    \item Students gain a basic understanding of how images are digitally stored and modified, how colors are created, what a pixel is, and how to manipulate these images.
\end{itemize}
\end{itemize}
Through the code they submit, as well as in their grading meeting, they should be able to demonstrate their understanding of the code that they wrote and the aforementioned computer science principles to at least a satisfactory degree.

In order to complete the project, students should be taught the following concepts:
\begin{itemize}
    \item Grids
    \item Boolean logic
    \item Managing tuples
    \item Digital images basics \item {\consolas pillow} methods
    \item Doubly nested for loops
    \item Bounds checking with grids
\end{itemize}

\end{document}
