\documentclass[11pt, letterpaper, onecolumn, oneside, final]{article}


\usepackage{handout}
\usepackage{soul}

\newfontfamily{\consolas}{Consolas}[Extension = .ttf]

\DocumentTitle {Project 0}
\DocumentSubtitle {Turtles!}
% End of preamble

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
    \maketitle


\section{Assignment Goals.} 

In this assignment, the students will be expected to demonstrate their understanding of the following concepts:
\begin{itemize}
\item \textbf{Turtle manipulation \& handling}
\begin{itemize}
\item Students should be able to use and explain basic Turtle methods, as given to them in labs and lectures.
\end{itemize}
\item \textbf{Introductory for loops}
\begin{itemize}
\item Students should demonstrate that they understand the flow of for loops and use them in a creative manner to achieve something that otherwise would require excessively long blocks of code. They should demonstrate that for loops allow them to condense their code and increase its complexity to solve their problems in an interesting way.
\end{itemize}
\item \textbf{Abstract use of Python arithmetic operators}
\begin{itemize}
\item Students may decide to not use arithmetic operators in their project, but by doing so
they will be able to successfully achieve the intent of this project by synthesizing many
basic concepts they have learned to produce a creative drawing. By using basic
arithmetic operators, they are able to create more intricate designs than imaginable
without the innovative use of these operators.
\end{itemize}
\item \textbf{Sequential program flow}
\begin{itemize}
\item Students should demonstrate an understanding of how programs flow from instruction to instruction, and through this they should be able at least make something simple with Turtles.
\end{itemize}
\item \textbf{Invocation of functions}
\begin{itemize}
\item While simple, students should show that they understand what functions are and how to call them.
\end{itemize}
\end{itemize}
Through the code they submit, as well as in their grading meeting, they should be able to demonstrate their understanding of the code that they wrote and the aforementioned computer science principles to at least a satisfactory degree.

In order to complete the project, students should be taught the following concepts:
\begin{itemize}
    \item Basics of writing and running programs
    \item Turtle Methods
    \item Types and Operators
    \item Basic for loops
\end{itemize}

\end{document}
